---
title: "HW3"
author: "Anh Doan(atd2354)"
output:   
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(ggplot2)
library(mosaic)
library(tidyverse)

gas <- read_csv("gasprices.csv")
sclass <- read_csv("sclass.csv")
nbc <- read_csv("nbc_pilotsurvey.csv")
ebay <- read_csv("ebay.csv")
```
[My GitHub Repository](https://github.com/anhdoan0611/HW3_SDS315)

# **Problem 1: Gas Prices**

### **Prices vs Competition In Sight**

- **Claim**: Gas stations charge more if they lack direct competition in sight.

- **Evidence**:

```{r}
#Set seed for reproducibility
set.seed(123)

#Bootstrap The Difference in Mean Gas Prices
avg_prices = do(10000)*diffmean(Price ~ Competitors, data=resample(gas))

#Graph the Bootstrap Sampling Distribution
ggplot(avg_prices) + 
  geom_histogram(aes(x= diffmean),color = "black", fill = "#045a8d") +
  labs(title = "Price Difference Bootstrap Distribution (Competition vs No Competition)",
       x = "Mean Difference",
       y = "Count") 

## a confidence interval: a range of plausible values based on the sampling distribution
confint(avg_prices, level=0.95)
```

- The bootstrap sampling distribution of the price differences centered around an estimated mean difference of **-0.02 dollars**. The difference in price between gas stations with or without competition in sight is somewhere between **-0.06** and **0.01 dollars**, with 95% confidence.

- **Conclusion**: The claim is unsupported by the data. While the point estimates that gas stations with no competition may charge **2.35** cents higher, the 95% confidence interval suggests the possibility of no difference, meaning that there is uncertainty in supporting the claim. 

### **Relationship Between Median Household Income and Price**

- **Claim**: The richer the area, the higher the gas prices

- **Evidence**:

```{r}
#Set seed for reproducibility
set.seed(123)

#Bootstrap the Correlation Between Income and Prices based on 10,000 resamples
income_prices <- do(10000) * {
  resampled_data <- resample(gas)
  cor(resampled_data$Price, resampled_data$Income)
}

#Graph the Bootstrap Sampling Distribution
ggplot(income_prices) +
  geom_histogram(aes(x = result), color = "black", fill = "#99d8c9", bins = 30) +
  labs(title = "Bootstrap Sampling Distribution of Correlation Between Income & Gas Prices",
       x = "Correlation",
       y = "Count")

## a confidence interval: a range of plausible values based on the sampling distribution
confint(income_prices, level=0.95)
```

- The bootstrap sampling correlation estimate is **0.396** dollars, suggesting a moderate positive relationship between these two variables. The 95% confidence interval for this correlation is between **0.20** and **0.57** dollars, which does not include 0.

- **Conclusion**: The claim is supported by data. There is moderate evidence that gas prices are higher in richer areas, indicated by the positive relationship. 

### **Prices vs Stop Lights**

- **Claim**: Gas stations at stoplights charge more

- **Evidence**: 

```{r}
#Set seed for reproducibility
set.seed(123)

#Bootstrap based on 10,000 resamples
avg_prices = do(10000)*diffmean(Price ~ Stoplight, data=resample(gas))

#Graph the Bootstrap Sampling Distribution
ggplot(avg_prices) + 
  geom_histogram(aes(x= diffmean),color = "black", fill = "#c51b8a") +
  labs(title = "Bootstrap Sampling Distribution of Price Differences (Stoplights vs No Stoplights)",
       x = "Mean Difference",
       y = "Count") 

## a confidence interval: a range of plausible values based on the sampling distribution
confint(avg_prices, level=0.95)
```

- The bootstrap sampling distribution centered around an estimated mean difference of **-0.003 dollars**. The difference in price between gas stations located at stoplights and those not located is between **-0.04** and **0.03 dollars**, indicating no statistically significant difference.

- **Conclusion**: The claim is unsupported by the data. The evidence does not provide a clear price difference between these two types of gas stations. 

### **Prices vs Direct Highway Access**

- **Claim**: Gas stations with direct highway access charges more

- **Evidence**:

```{r}
#Set seed for reproducibility
set.seed(123)

#Bootstrap based on 10,000 resamples
avg_prices = do(10000)*diffmean(Price ~ Highway, data=resample(gas))

#Graph the Bootstrap Sampling Distribution
ggplot(avg_prices) + 
  geom_histogram(aes(x= diffmean),color = "black", fill = "#d95f02") +
  labs(title = "Bootstrap Sampling Distribution of Price Differences (Highway vs No Highway)",
       x = "Mean Difference",
       y = "Count") 

## a confidence interval: a range of plausible values based on the sampling distribution
confint(avg_prices, level=0.95)
```

- The estimate for the mean difference is **0.05 dollars**. The difference in gas prices between stations with or without highway access is between **0.01** and **0.08 dollars**, with 95% confidence, indicating price difference.

- **Conclusion**: Since the 95% confidence interval does not include zero, the claim is supported by the data, suggesting that gas stations with direct highway access charges more.

### **Shell vs Non-Shell Brands**

- **Claim**: Shell charges more than all other non-Shell brands

- **Evidence**:

```{r}
#Set seed for reproducibility
set.seed(123)

#Make a "Shell" variable
gas_subset = mutate(gas, Shell = ifelse(Brand == "Shell", yes = TRUE, no = FALSE))

#Bootstrap based on 10,000 resamples
gas_brand = do(10000)*diffmean(Price ~ Shell, data = resample(gas_subset))

#Graph the Bootstrap Sampling Distribution
ggplot(gas_brand) + 
  geom_histogram(aes(x= diffmean),color = "black", fill = "#8da0cb") +
  labs(title = "Bootstrap Sampling Distribution of Price Differences (Shell vs Non-Shell Brands)",
       x = "Mean Difference",
       y = "Count") 

## a confidence interval: a range of plausible values based on the sampling distribution
confint(gas_brand, level=0.95)
```

- The bootstrap sampling distribution shows an estimated mean difference of **0.03 dollars**. The difference in gas prices between Shell and non-Shell gas stations is between **-0.01** and **0.07 dollars**, with 95% confidence.

- **Conclusion**: Since the 95% confidence interval includes zero, it indicates no statistically significant difference. Therefore, the claim is unsupported by the data.

# **Problem 2: Mercedes S-Class**

### **Average Mileage of 2011 S-Class 63 AMGs**

```{r}
#Set seed for reproducibility
set.seed(123)

#Filter those cars where year = "2011" and trim = "63 AMG"
sclass_subset1 = filter(sclass, year == 2011 & trim == "63 AMG")

#Bootstrap the average mileage based on 10,000 resamples
avg_mileage = do(10000)*mean(~mileage, data=resample(sclass_subset1))

#Histogram of the 10,000 different estimates
ggplot(avg_mileage) + 
  geom_histogram(aes(x=mean), color = "black", fill = "darkred") +
  labs(title = "Bootstrap Distribution for the Average Mileage of 2011 S-Class 63 AMGs",
       y = "Count",
       x = "Average Mileage") +
  scale_x_continuous(
    breaks = seq(24000,36000, by = 2000))

## a confidence interval: a range of plausible values based on the sampling distribution
confint(avg_mileage, level=0.95)
```

- The average mileage of 2011 S-Class 63 AMGs that were hitting the used-car market is between **26322** and **31863 miles**, with 95% confidence.

### **Proportion of Black 2014 S-Class 550s**

```{r}
#Set seed for reproducibility
set.seed(123)

#Filter those cars where year == "2014" and trim = "550"
sclass_subset2 = filter(sclass, year == 2014 & trim == "550")
sclass_subset2 <- mutate(sclass_subset2, is_black = (color == "Black"))

#Bootstrap the proportion of black 2014 S-Class 550s
prop_black = do(10000)*prop(~is_black, data=resample(sclass_subset2))

#Histogram of the 10,000 different estimates
ggplot(prop_black) +
  geom_histogram(aes(x=prop_TRUE), color = "black", fill = "darkgreen") +
  labs(title = "Bootstrap Sampling Distribution for Proportion of Black 2014 S-Class 550s",
       x = "Proportion of Black Cars",
       y = "Count")

## a confidence interval: a range of plausible values based on the sampling distribution
confint(prop_black, level=0.95)
```

- The proportion of all 2014 S-Class 550s that were painted black is between **41.71%** and **45.28%**, with 95% confidence.

# **Problem 3: NBC Viewer Survey**

### **Difference in Mean Viewer Happy Response between "Living with Ed" and "My Name is Earl" **

- **1. Question**: What is the difference in viewer happiness between the shows "Living with Ed" and "My Name is Earl"? Does one show consistently produces a higher mean happy response among viewers?

- **2. Approach**: Using Monte Carlo simulations, I performed 10000 bootstrap resamples to estimate the difference in mean happy responses between the two shows. Then, I used statistical inference to construct a 95% confidence interval.

- **3. Results**:

```{r}
#Set seed for reproducibility
set.seed(123)

#Filter "Living with Ed" and "My Name is Earl" shows
nbc_subset1 <- filter(nbc, Show == "Living with Ed" | Show == "My Name is Earl")

#Bootstrap the difference in Mean Happiness
prop_happy = do(10000)*diffmean(Q1_Happy ~ Show, data=resample(nbc_subset1))

#Histogram of the 10,000 different estimates
ggplot(prop_happy) +
  geom_histogram(aes(x=diffmean), color = "black", fill = "#016c59") +
  labs(title = "Bootstrap Sampling Distribution for Difference in Mean Happiness",
       x = "Difference in Mean Happiness",
       y = "Count")

## a confidence interval: a range of plausible values based on the sampling distribution
confint(prop_happy, level=0.95)
```

- The estimated difference in mean happiness reponses between these two shows is **-0.15**. The difference in mean happiness reponses is between **-0.40** and **0.01**, with 95% confidence.

- **4. Conclusion**: Since the 95% confident interval includes zero, it suggests that there is no strong evidence that one show consistently produces a higher mean happiness response among viewers.

### **Difference in Mean Viewer Annoyed Response between "The Biggest Loser" and "The Apprentice: Los Angeles"**

- **1. Question**: What is the difference in viewer annoyance between the shows "The Biggest Loser" and "The Apprentice: Los Angeles"? Does one show consistently produces a higher mean annoyed response among viewers?

- **2. Approach**: Using Monte Carlo simulations, I performed 10000 bootstrap resamples to estimate the difference in mean annoyed responses between the two shows. Then, I used statistical inference to construct a 95% confidence interval.

- **3. Result**: 

```{r}
#Set seed for reproducibility
set.seed(123)

#Filter the data set
nbc_subset2 <- filter(nbc, Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")

#Bootstrap the difference in Mean Annoyance
prop_annoy = do(10000)*diffmean(Q1_Annoyed ~ Show, data=resample(nbc_subset2))

#Histogram of the 10,000 different estimates
ggplot(prop_annoy) +
  geom_histogram(aes(x=diffmean), color = "black", fill = "darkorange") +
  labs(title = "Bootstrap Sampling Distribution for Difference in Mean Annoyance",
       x = "Difference in Mean Annoyance",
       y = "Count")

## a confidence interval: a range of plausible values based on the sampling distribution
confint(prop_annoy, level=0.95)
```

- The estimate of the mean difference is **-0.27**. The mean difference in annoyed responses between these two shows is between **-0.53** and **-0.02**, with 95% confidence. The 95% confidence interval does not include zero.

- **Conclusion**: Based on the 95% confidence interval, viewers of "The Apprentice: Los Angeles" consistently feel more annoyed. 

### **Proportion of Confused Viewers of "Dancing With The Stars"**

- **1. Question**: What proportion of American TV watchers would we expect to give "Dancing With The Stars" a response of 4 or greater on the "Q2_Confusing" question?

- **2. Approach**: Using Monte Carlo simulations, I performed 10000 bootstrap resamples to estimate the proportion of viewers who gave a response of 4 or 5 on the "Q2_Confusing" question. Then, I used statistical inference to construct a 95% confidence interval.

- **3. Evidence**: 

```{r}
#Set seed for reproducibility
set.seed(123)

#Filter the data for "Dancing With The Stars" responses
nbc_subset3 <- filter(nbc, Show == "Dancing with the Stars")
nbc_subset3 <- mutate(nbc_subset3, Confused = (Q2_Confusing >= 4))

#Bootstrap the proportion of confused viewers
prop_confused = do(10000)*prop(~Confused, data=resample(nbc_subset3))

#Graph the sampling distribution
ggplot(prop_confused) + 
  geom_histogram(aes(x=prop_TRUE), fill = "darkblue", color = "black") +
  labs(title = "Sampling Distribution for Proportion of Confused Viewers",
       x = "Proportion",
       y = "Count")

## a confidence interval: a range of plausible values based on the sampling distribution
confint(prop_confused, level=0.95)
```

- The 95% confidence interval for the proportion of viewers who found the show confusing (responses of 4 or 5) is from **3.87%** to **11.60%**, with an estimate of **7.73%**

- **4. Results**: Based on the 95% confidence interval, we can estimate that between **3.87%** and **11.60%** of American TV watchers would give a response of 4 or greater to the “Q2_Confusing” question?

# **Problem 4: Ebay**

- **1. Question**: Does paid search advertising on Google creates extra revenue for EBay?

- **2. Approach**: Using Monte Carlo simulations, I performed 10000 bootstrap resamples to estimate the difference in revenue ratio between the treatment and control DMAs. Then, I used statistical inference to construct a 95% confidence interval.

- **3. Evidence**:

```{r}
#Create a new revenue_ratio and control variable 
ebay = mutate(ebay, revenue_ratio = rev_after/rev_before)
ebay_subset = mutate(ebay, Control = ifelse(adwords_pause == 1, yes = TRUE, no = FALSE)) 

#Bootstrap the mean difference 
ebay_experiment = do(1000)*diffmean(revenue_ratio ~ Control, data = resample(ebay_subset))

#Graph the Bootstrap Sampling Distribution
ggplot(ebay_experiment) +
  geom_histogram(aes(x=diffmean), color = "black", fill = "#43a2ca") +
  labs(title = "Sampling Distribution of Revenue Ratio Difference",
       x = "Mean Difference",
       y = "Count")

confint(ebay_experiment, level = 0.95)
```

- The estimated mean difference in revenue ratios between the treatment and control groups is **-0.05**. The mean difference in revenue ratios between these 2 groups is between **-0.09** and **-0.01**, with 95% confidence. The 95% confidence interval does not include zero.

- **4. Conclusion**: Based on the 95% confidence interval, the treatment group had a lower revenue ratio compared to the control group, suggesting that paid search advertising on Google creates extra revenue for EBay.
